### 2014-10-13 fundamentals/intro.tex
improvements to intro

In order to characterize the performance of nuclear fuel cycle tecnhologies and performance metrics, nuclear fuel cycle analysis 
requires calculation and optimization of myriad physical, nuclear, chemical, 
industrial, and political phenomena. Furthermore, complex systems such as 
nuclear process physics, facility deployment, and material routing each 
must be modeled simultaneously for even the simplest of nuclear fuel cycle 
simulations.

% MJG - I'm hesitant about using the phrase 'full detail'. I think we can be
% more precise.

>>>>

As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance on technical, economic, political, and environmental axes increases 
in importance. In order to characterize the performance of nuclear fuel cycles, 
nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
chemical, industrial, and political 
phenomena. Coupled simulation of complex systems such as nuclear process physics, 
facility deployment, and material routing
for even the simplest of nuclear fuel cycle simulations.
